\documentclass{beamer}

\mode<presentation> {


\usetheme{Madrid}


\setbeamertemplate{footline}[page number]

\setbeamertemplate{navigation symbols}{} }

\usepackage{graphicx} 
\usepackage{booktabs} 
\usepackage{tkz-graph}
\GraphInit[vstyle = Shade]
\tikzset{
  LabelStyle/.style = { rectangle, rounded corners, draw,
                        minimum width = 2em, fill = yellow!50,
                        text = red, font = \bfseries },
  VertexStyle/.append style = { inner sep=5pt,
                                font = \normalsize\bfseries},
  EdgeStyle/.append style = {->, bend left} }
\usetikzlibrary {positioning}

\definecolor {processblue}{cmyk}{0.96,0,0,0}


\title[Short title]{WE Portal} 


\author{Hetal Kuvadia}


\date{\today} 

\begin{document}

\begin{frame}
\titlepage 
\end{frame}


\section{What is the project?}
\begin{frame}{What is the project?}
        A portal to connect companies and the best women in engineering.

\end{frame}

\begin{frame}{Why is it required?}
\begin{itemize}
    \item  To build a strong community for women in technology.
    \pause
    \item The companies can hire the best women.

\end{itemize}
\end{frame}

\begin{frame}{Modules}
    \begin{itemize}
        \item Student
		\item Faculty
		\item Companies
    \end{itemize}
\end{frame}

\begin{frame}{Technology Stack}
    \begin{itemize}
        \item Backend: Django
		\item Frontend: HTML, CSS, JS
		\item Database: SQL
    \end{itemize}
\end{frame}

\begin{frame}{Time Line}
    \begin{itemize}
        \item By June 26th 2019 the prototype will be ready.
        \item Improvements will be done during the internship period of two weeks.
    \end{itemize}
\end{frame}

\begin{frame}{Future Prospect}
   
    \begin{center}
        Generalize this module and add it to the Open Edx.
    \end{center}
        
    
\end{frame}

\begin{frame}
    \begin{center}
        Questions?
    \end{center}
\end{frame}
\end{document}

